---
title: "Key Drivers Analysis"
description: "description"
author:
  - name: Dan Yavorsky
    url: danyavorsky.com
    orcid: 0000-0003-4095-6405
date: 2023-03-31
draft: true
---


Key drivers analysis is an umbrella term used to describe methods that calculate relative importance scores for a group of predictors that are associated with an outcome variable.

Let's use the Boston dataset from the MASS package which provides the following information:

 - `medv`: median value of owner-occupied homes in $1000s.
 - `crim`: per capita crime rate by town.
 - `zn`: proportion of residential land zoned for lots over 25,000 sq.ft.
 - `indus`: proportion of non-retail business acres per town.
 - `chas`: Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).
 - `nox`: nitrogen oxides concentration (parts per 10 million).
 - `rm`: average number of rooms per dwelling.
 - `age`: proportion of owner-occupied units built prior to 1940.
 - `dis`: weighted mean of distances to five Boston employment centres.
 - `rad`: index of accessibility to radial highways.
 - `tax`: full-value property-tax rate per $10,000.
 - `ptratio`: pupil-teacher ratio by town.
 - `black`: 1000(Bk - 0.63)^2 where BkBk is the proportion of blacks by town.
 - `lstat`: lower status of the population (percent).




> TODO: 
> review Belsley D.A., Kuh, E. and Welsch, R.E. (1980) Regression Diagnostics. Identifying Influential Data and Sources of Collinearity. New York: Wiley. 
> online here: https://onlinelibrary.wiley.com/doi/abs/10.1002/jae.3950040108
> review Harrison, D. and Rubinfeld, D.L. (1978) Hedonic prices and the demand for clean air. J. Environ. Economics and Management 5, 81–102.
> oneline here: https://www.law.berkeley.edu/files/Hedonic.PDF


```{r}
data(Boston, package="MASS")
```

### Pearson Correlations

```{r}

```


### Standardized Coefficients

```{r}

```


### Permutation-Based

```{r}

```


### LMG/Shapley Values for Linear Regression

```{r}

```


### Johnson's Relative Weights

```{r}

```


### Random Forest: Mean Decrease in Gini Coefficient

```{r}

```


### XGBoost: --describe--

```{r}

```




